Signatures of Foreground Sky in Power Spectra of Redshifted Neutral Hydrogen from the Epoch of Reionization

### 2014-09-05 foreground_delay_spectrum_modeling.tex
From danny1: ===========
(*) Fixed the citation labels included by Danny
(*) Added a bibtex entry to the eor.bib for an additional reference
(*) Added empty sections 'Discussion' and 'Conclusions' just to compile without
errors

---------------------------------------------------------------------------------
From v0.3.2:
===========

(*) Danny changed abstract and intro and also replaced interferometer with
baseline to match vernacular usage
(*) Danny added a few additional references
(*) Danny made a few other miscellaneous edits
(*) Nithya pulled Danny's version into a branch danny1

Foregrounds work their way into the power spectrum by either having intrinsic spectral variability, high instrumental chromaticity, or through approximations in the estimating the power spectrum. Here we are focusing on the instrumental effects. To de-couple from possible analysis effects, such as those pointed out by \citet{Haz13}, we compute power spectra using the per-baseline approach of \citet{pob13,arp14}.  This approximates the power spectrum as the fourier transform of the spectra output by the correlator.

@@

% \section{Discussion}\label{sec:discussion}

>>>>

Foregrounds work their way into the power spectrum by either having intrinsic spectral variability, high instrumental chromaticity, or through approximations in the estimating the power spectrum. Here we are focusing on the instrumental effects. To de-couple from possible analysis effects, such as those pointed out by \citet{haz13}, we compute power spectra using the per-baseline approach of \citet{pob13,par14}.  This approximates the power spectrum as the fourier transform of the spectra output by the correlator.

@@

\section{Discussion}\label{sec:discussion}

\section{Conclusion}\label{sec:conclusion}
